The Practical Application of MST

### 2021-02-23 article.Rmd
Added IIC

$$
I_i(\theta, b_i) = P_i(\theta, b_i)Q_i(\theta, b_i)
$$

@@

>>>>

$$
I_i(\theta, b_i) = P_i(\theta, b_i)Q_i(\theta, b_i)
$$
Where P is the probability of getting the item correct (for a given ability), and Q is the probability of getting it wrong.

@@

The IIF can be represented visually like this, using the `plot` function from the `ltm` package:

```{r}
itemNo <- 7
itemID <- str_extract(rownames(df_difficulties)[itemNo], "Item\\d+")
itemDifficulty <- df_difficulties[itemNo]
itemPlot <- data.frame(plot(raschmodel, type = "IIC", items = itemNo, plot = FALSE))
colnames(itemPlot) <- c('theta', 'information')
ggplot(itemPlot, aes(x=theta, y=information)) + 
  geom_line() +
  labs(title="Item Information Function", x="θ", y="I(θ)")
```
